%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATION
%-------------------------------------------------------------------------------
\input{content/configuration.tex}


% PDF Metadata for cover letter
\hypersetup{%
  pdftitle={Josh Vaughen's Cover Letter for Maximus},
  pdfauthor={Josh Vaughen, Machine Learning Engineer},
  pdfsubject={Cover letter for Senior Analytics Engineer position at Maximus},
  pdfkeywords={Cover letter, Machine Learning Engineer, Senior Analytics Engineer, Maximus, Josh Vaughen}
}

%-------------------------------------------------------------------------------
% HEADER FOR PERSONAL INFORMATION
%-------------------------------------------------------------------------------
\input{content/personal.tex}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Maximus Recruitment Team}
  {Maximus\\Santa Monica, CA}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Senior Analytics Engineer}
% How the letter is opened
\letteropening{To whom it may concern,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Resume}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[L]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Josh Vaughen{\enskip•\enskip}Cover Letter written in {\LaTeX{}}}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About me}
%\input{content/aboutme.tex}
I'm an engineer who's all about tech, travel, and fitness—and chasing challenges that make me better, inside and out. Whether it's debugging code, exploring a new country, or crushing a workout, I'm always looking for the next way to level-up.

Last year, I hit pause on work to take a solo journey around the world and truly experience life. Sixty countries, countless adventures, and more life lessons than I can count later... I came back with a deeper understanding of people, cultures, and myself. 

\lettersection{Why Maximus?}
I came across Maximus a few months ago and recently started the TRT + EP protocol. Through every contact point I have had with my doctor, Dr. Cam, customer support (Melody), and the Discord server I have been continuously impressed by the \textit{get shit done} work ethic Maximus employees exude. I get the sense that folks there really take ownership of their work, are driven to succeed, and are passionate about helping men in their own journeys to succeed.

I am working to get back into employment and to improve myself personally and professionally. I want to surround myself with colleagues who are driven to grow and succeed, and make a difference, and this aligns with my impression of Maximus.

\lettersection{Why me?}
Most of my career has been spent in big-tech working as a Data Scientist and later as a Machine Learning Engineer. I have extensive experience with developing and deploying data engineering pipelines at web scale. I have run experiments that have significantly improved conversion rates and revenue. I have developed and deployed machine learning models that have personalized product and marketing experiences. I have worked with product, marketing, and engineering teams through many release cycles. I am confident I would excel in this role.

Perhaps more importantly to me and why I am applying: I believe in the mission of Maximus. Physical fitness and achieving my maximum potential is integral to who I am. I'm looking for employment that not only challenges me professionally, but also personally. Being part of an organization that is full of driven people and helps men achieve their potential aligns with my values and aspirations.

I hope you will take my application into consideration. 

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
