%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
%\cvsection{Work Experience}

% For the purposes of interview preparation, we want to include on each bullet
% point in the resume a commented section with the following:
%
% - problem definition
% - possible approaches
% - what approach was taken and why
% - what technologies were used in that approach and why
% - results of that approach
% - what was learned from that experience
% - what would be done differently next time
% - what was the business impact of that work
% 
% This will be filled out for each of the below bullet points in the resume

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Graduate Teaching Assistant} % Job title
    {University of California, Los Angeles} % Organization
    {Los Angeles, California} % Location
    {Mar. 2015 - Jun. 2016} % Date(s)
    {I was a Graduate Teaching Assistant for CS35L Software Construction Laboratory. I led lectures and labs several times a week, as well as held recurring office hours and review sessions before exams.} % Overall description
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led lecture 3x weekly, office hours 2x weekly}
        \item {Wrote and graded homework and exams}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Engineering Intern - Mobile App Development} % Job title
    {Adobe} % Organization
    {San Jose, California} % Location
    {Jun. 2015 - Sep. 2015} % Date(s)
    {Joined the Acrobat iOS team to grow my knowledge of iOS and watchOS. Developed a prototype Apple Watch integration with Acrobat that was ahead of its time. Worked on initial Dropbox integration with Acrobat.} % Overall description
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Proposed and developed a prototype presentation control companion application for Acrobat on the Apple Watch}
        \item {Utilized Core Motion API to detect and react to hand gestures, allowing user to control their presentation without button pressing}
        \item {Worked on initial Dropbox cloud provider filesystem integration within Acrobat iOS}
        \item {Winner of the 2015 Intern Project Expo in San Jose for the second year in a row for Apple Watch work}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Engineering Intern - Mobile App Development} % Job title
    {Adobe} % Organization
    {San Jose, California} % Location
    {Jun. 2014 - Sep. 2014} % Date(s)
    {Joined the Adobe Sign team to develop the iOS application. Learned iOS and general software development methodologies on the fly.} % Overall description
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented four new features, fixed several existing bugs, improved usability of several interfaces}
        \item {Designed, implemented, and demoed a new prototype Sign UI/UX for my HackWeek project}
        \item {Wrote automated tests for iPhone/iPad on new Appium-based automation framework}
        \item {Completed Green Belt security training for C/C++ developers}
        \item {Winner of the 2014 Intern Project Expo in San Jose for UI/UX and automation work}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software QA Engineering Intern} % Job title
    {Aruba Networks, an HPE Company} % Organization
    {Sunnyvale, California} % Location
    {Jun. 2013 - Dec. 2013} % Date(s)
    {Joined the hardware automation team at Aruba to develop an automated testing platform based on commodity hardware (Raspberry Pi, Roomba robots) and a pan-tilt servo system. This platform was used to automate physical world interaction and 802.11 RF tests.} % Overall description
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote a controlling wrapper API over existing Roomba microcode to simplify and more robustly control the platform}
        \item {Wrote orchestration platform and API to automate control of six free-roaming robots, effectively swarm control, including collision detection and avoidance}
        \item {Wrote controlling API for commodity pan-tilt servo system such that RF heatmaps could be profiled in multiple orientations via automation}
        \item {Successfully completed ACMA and ACMP certification courses}
        \item {Presented project outcomes at Aruba Tech Talk; was the Featured Intern on corporate blog}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Engineering Intern} % Job title
    {Galil Motion Control} % Organization
    {Rocklin, California} % Location
    {Jun. 2012 - Sep. 2012} % Date(s)
    {Joined the Research and Development Engineering team to build an automated firmware verification and testing system. I also developed tooling frameworks for the now-released GalilSuite application.} % Overall description
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Rewrote existing test software reducing execution time in half}
        \item {Wrote automated firmware verification system with ability to simultaneously support tens of controllers}
        \item {Wrote portable (Windows/Linux) tool for GalilSuite server API audits}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
