%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

% For the purposes of interview preparation, we want to include on each bullet
% point in the resume a commented section with the following:
%
% ** Problem definition:
% 
% 
% ** Solution:
%
%
% ** Results and business impact:
%
%
% ** What was learned:
%
% 
% This will be filled out for each of the below bullet points in the resume

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {World Explorer} % Job title
    {Sabbatical} % Organization
    {Earth} % Location
    {Apr. 2023 - Present} % Date(s)
    {\parbox[t]{\linewidth}{After a life-altering medical event, I took a sabbatical to nearly 60 countries, developing proficiency in two languages and enriching my cultural understanding. This experience honed my adaptability and problem-solving skills, enhancing my effectiveness in fast-paced, results-driven environments.}} % Overall description
    {}

%---------------------------------------------------------
\cventry
    {Machine Learning Engineer IV} % Job title
    {Adobe} % Organization
    {Seattle, WA} % Location
    {Jan. 2020 - Apr. 2023} % Date(s)
    {Developed models and data engineering systems to enhance user onboarding experiences, personalization, and upsell strategies for Acrobat.} % Overall description
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Constructed latent variable model to improve new user onboarding, leading to increased activation and subscription rates}
        \item {Architected a containerized data engineering production system used for personalization of millions of in-product and email experiences}
        \item {Utilized XGBoost to identify primary factors influencing customer attrition and guided retention strategies with product teams}
        \item {Refined an implementation of the apriori algorithm to handle larger datasets, optimizing for both computational complexity and rule granularity}
        \item {Implemented a shared Python library, Docker containers, and a standard data model to unify and support team operational activities across projects}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Data Scientist III} % Job title
    {Adobe} % Organization
    {San Jose, CA} % Location
    {Jan. 2018 - Jan. 2020} % Date(s)
    {Deployed and analyzed A/B tests, developed pricing models, and led activation and retention modeling for Acrobat.} % Overall description
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Leveraged collaborative filtering and content-based filtering techniques to refine tool recommendations, increasing user engagement}
        \item {Used conjoint analysis to improve feature bundling and pricing, increasing revenue and motivating new SKU offerings}
        \item {Applied cohort and churn analysis techniques on users, features, and subscriptions to uncover activation and retention factors}
        \item {Designed, deployed, and analyzed A/B tests focused on revenue impact, materially increasing subscription counts and ARR}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Data Scientist II} % Job title
    {Adobe} % Organization
    {San Jose, CA} % Location
    {Aug. 2016 - Jan. 2018} % Date(s)
    {Implemented a KPI reporting and analytics framework for Acrobat, Sign, and Scan; including data engineering and an alert system for detected issues.} % Overall description
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted in-product A/B tests designed to increase sign-in rates, resulting in the majority of all users transitioning from anonymous to signed-in}
        \item {Created an anomoly detection system leveraging ARIMA and STL decomposition methods, which identified several previously unknown major issues}
        \item {Developed a unified KPI reporting framework and system based on SMART goals that was adopted across the organization to drive data strategy}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
