%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activities}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Volunteer Interviewer} % Affiliation/role
    {Year Up} % Organization/group
    {Seattle, WA} % Location
    {Nov. 2021} % Date(s)
    {Volunteered with Year Up to conduct mock interviews, helping underrepresented youth gain practical experience and prepare for successful careers.} % Overall Description
    {}

%---------------------------------------------------------
  \cventry
    {Technical Volunteer} % Affiliation/role
    {Adobe Tech Summit} % Organization/group
    {San Jose, CA} % Location
    {Feb 2017. - Feb 2019} % Date(s)
    {Volunteered to run the Adobe Tech Summit Robot Challenge, providing technical guidance and support to contestants on rules and development.} % Overall Description
    {}

%---------------------------------------------------------
  \cventry
    {Team Mentor} % Affiliation/role
    {First Robotics} % Organization/group
    {Lincoln, CA} % Location
    {Jan 2009. - Apr 2014} % Date(s)
    {Founded and mentored FIRST Robotics team 3257, guiding high school students in designing and programming robots for the FRC competitions.} % Overall Description
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Volunteered hundreds of hours to instruct high school students in robotics concepts as part of the FIRST Robotics Competition (FRC) program}
            \item {Promoted professionalism and soft skills among students throughout the six-week build season, fostering effective teamwork and leadership}
            \item {Supported the Sacramento Regional Competition by facilitating pit organization and ensuring smooth event operations for the FRC community}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Volunteer Instructor} % Affiliation/role
    {IEEE} % Organization/group
    {Riverside, CA} % Location
    {Apr. 2012} % Date(s)
    {Volunteer for IEEE Merit Badge Day, instructing Boy Scouts in areas of engineering, energy, robotics, electronics, and more for their merit badges.} % Overall Description
    {}

%---------------------------------------------------------
\end{cventries}
