%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Organizations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Member, Secretary, Webmaster} % Position title
    {Tau Beta Pi} % Organization
    {Davis, CA} % Location
    {Jun. 2012 - Present} % Date(s)
    {Served as webmaster, rebuilding the Davis Tau Beta Pi website, and as secretary, coordinating communication between national headquarters and the local chapter. As an alumnus, continue to participate in volunteer events and chapter activities.} % Overall description
    {}

%---------------------------------------------------------
\cventry
    {Member} % Position title
    {Institute of Electrical and Electronics Engineers (IEEE)} % Organization
    {Riverside, CA} % Location
    {Sep. 2010 - Present} % Date(s)
    {Volunteered for IEEE Boy Scouts Merit Badge Day, Micromouse robotics workshops, peer tutoring, and various chapter activities.} % Overall description
    {}

%---------------------------------------------------------
\cventry
    {Member} % Position title
    {Association for Computing Machinery (ACM)} % Organization
    {Riverside, CA} % Location
    {Sep. 2010 - Present} % Date(s)
    {Habitual peer tutoring, chapter professional events, and other chapter activities.} % Overall description
    {}

%---------------------------------------------------------
\cventry
    {Member} % Position title
    {Golden Key International Honor Society} % Organization
    {Riverside, CA} % Location
    {Dec. 2011 - Present} % Date(s)
    {Member of Golden Key International Honor Society, recognizing academic excellence, leadership, and commitment to service.} % Overall description
    {}

%---------------------------------------------------------
\cventry
    {Member} % Position title
    {National Society of Collegiate Scholars} % Organization
    {Riverside, CA} % Location
    {Feb. 2011 - Present} % Date(s)
    {Member of the National Society of Collegiate Scholars, recognizing academic excellence and leadership among high-achieving students.} % Overall description
    {}

%---------------------------------------------------------
\end{cventries}